On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-20 main.tex
update evaluation

\subsection{Evaluation}\label{sec:performance-implementation}
\begin{table}
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &   0.19 &   0.18 & 0.17 & 0.21 &    5.82 \\
    e250b5p10eq    &   0.21 &   0.18 & 0.24 & 0.34 &    2.83 \\
    e500b5p50ne    &   0.23 &   0.22 & 0.25 & 0.28 &   37.28 \\
    e500b5p50eq    &   0.26 &   0.21 & 0.24 & 0.34 &   14.06 \\
    e1000b10p100ne &   0.31 &   0.37 & 0.42 & 0.52 & timeout \\
    e1000b10p100eq &   0.37 &   0.28 & 0.35 & 0.52 &   77.83 \\
    e2000b20p200ne &   1.50 &   2.75 & 0.84 & 1.11 & timeout \\
    e2000b20p200eq &   3.34 &   3.03 & 0.51 & 1.30 & timeout \\
    e3000b30p200ne &   1.75 &  26.38 & 1.59 & 2.29 & timeout \\
    e3000b30p200eq &  17.86 &  22.59 & 0.81 & 2.02 & timeout \\
    degenerate     & 220.53 & 232.63 & 0.28 & 0.37 & timeout
\end{tabular}
\caption{Total Time Usage (seconds)}\label{tab:benchmark-time}
\end{table}
\begin{table}
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    &  15.36 &   14.76 &  6.81 &  7.02 &  114.06 \\
    e250b5p10eq    &  15.56 &   14.95 &  7.06 &  7.25 &  100.48 \\
    e500b5p50ne    &  16.26 &   15.49 &  7.02 &  6.99 &  524.89 \\
    e500b5p50eq    &  17.97 &   15.54 &  7.07 &  7.01 &  546.91 \\
    e1000b10p100ne &  18.36 &   21.41 &  8.43 &  8.07 & timeout \\
    e1000b10p100eq &  20.41 &   17.66 &  8.69 &  7.63 & 5822.66 \\
    e2000b20p200ne & 239.71 &  283.45 & 13.54 & 12.27 & timeout \\
    e2000b20p200eq & 107.92 &  102.46 & 13.20 & 13.84 & timeout \\
    e3000b30p200ne & 112.59 & 1235.46 & 21.69 & 20.33 & timeout \\
    e3000b30p200eq & 245.92 &  228.85 & 21.79 & 18.33 & timeout \\
    degenerate     & 631.47 & 1229.30 & 19.75 & 18.57 & timeout
\end{tabular}
\caption{Peak Memory Usage (megabytes)}\label{tab:benchmark-memory}
\end{table}

@@

We observe that all variants of DV and TC perform better than SymKAT in terms of time and memory usage. When comparing the solver backends, BDD is marginally faster than SAT for smaller benchmarks, however, BDD's time and memory usage increases considerably for larger benchmarks. On the other hand, the performance of SAT is stable for all benchmarks. Furthermore, we have encountered degenerative expression pairs (the `degenerate' benchmark) which greatly reduce BDD performance but can be efficiently checked by SAT. We did not encounter any expression pairs where BDD performed significantly better than SAT.

>>>>

\subsection{Evaluation}\label{sec:performance-implementation}
\begin{table}
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    & 0.18   & 0.18   & 0.16 & 0.17 &    5.82 \\
    e250b5p10eq    & 0.19   & 0.18   & 0.15 & 0.18 &    2.83 \\
    e500b5p50ne    & 0.21   & 0.21   & 0.21 & 0.22 &   37.28 \\
    e500b5p50eq    & 0.22   & 0.21   & 0.20 & 0.27 &   14.06 \\
    e1000b10p100ne & 0.26   & 0.28   & 0.34 & 0.38 & timeout \\
    e1000b10p100eq & 0.28   & 0.26   & 0.28 & 0.41 &   77.83 \\
    e2000b20p200ne & 1.32   & 2.60   & 0.68 & 0.79 & timeout \\
    e2000b20p200eq & 1.92   & 2.95   & 0.41 & 1.00 & timeout \\
    e3000b30p200ne & 1.57   & 24.86  & 1.30 & 1.60 & timeout \\
    e3000b30p200eq & 10.82  & 22.83  & 0.66 & 1.54 & timeout \\
    degenerate     & 99.48  & 228.16 & 0.24 & 0.30 & timeout
\end{tabular}
\caption{Total Time Usage (seconds)}\label{tab:benchmark-time}
\end{table}
\begin{table}
\footnotesize
\centering
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l r r r r r}
    Benchmark & DV$_{\textsf{BDD}}$ & TC$_{\textsf{BDD}}$ & DV$_{\textsf{SAT}}$ & TC$_{\textsf{SAT}}$ & SK \\
    \hline
    e250b5p10ne    & 15.17  & 14.54   & 7.07  & 7.01  &  114.06 \\
    e250b5p10eq    & 15.69  & 14.69   & 7.06  & 7.29  &  100.48 \\
    e500b5p50ne    & 15.99  & 15.33   & 7.02  & 7.29  &  524.89 \\
    e500b5p50eq    & 16.85  & 15.26   & 6.99  & 7.01  &  546.91 \\
    e1000b10p100ne & 17.51  & 21.31   & 7.78  & 7.50  & timeout \\
    e1000b10p100eq & 19.52  & 17.48   & 8.17  & 7.04  & 5822.66 \\
    e2000b20p200ne & 237.17 & 280.70  & 12.95 & 11.43 & timeout \\
    e2000b20p200eq & 107.61 & 102.18  & 12.76 & 13.25 & timeout \\
    e3000b30p200ne & 112.06 & 1232.24 & 21.00 & 19.30 & timeout \\
    e3000b30p200eq & 245.23 & 228.86  & 21.18 & 17.64 & timeout \\
    degenerate     & 632.70 & 1225.24 & 19.13 & 17.94 & timeout
\end{tabular}
\caption{Peak Memory Usage (megabytes)}\label{tab:benchmark-memory}
\vspace{-1em}
\end{table}

@@

We observe that DV performs better than TC consistently when both algorithms use the same solver backend and all variants of DV and TC perform better than SymKAT. When comparing the solver backends, BDD and SAT perform similarly for smaller benchmarks, however, BDD's time and memory usage increase considerably for larger benchmarks. On the other hand, the performance of SAT is stable for all benchmarks. Furthermore, we have encountered degenerative expression pairs (the `degenerate' benchmark) which greatly reduce BDD performance but can be efficiently checked by SAT. We did not encounter any expression pairs where BDD performed significantly better than SAT.
